%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

%\cventry
%{Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
%{R.O.K Cyber Command, MND} % Organization
%{Seoul, S.Korea} % Location
%{Aug. 2014 - Exp. Apr. 2016} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
%\item {Improved functionality on military command and control system for incident response with Java Servlet.}
%\item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
%\end{cvitems}
%}

%------------------------------------------------

\cventry
{Senior Security Engineer, Android Malware Research} % Job title
{Google} % Organization
{Seattle, WA} % Location
{Sept. 2022 - Current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Developed scalable solutions to detecting malware on the Google Play store}
    \item {Developed "Red Team" style applications for auditing detection capabilities}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Security Engineer, Malware Reverse Engineer} % Job title
{Meta} % Organization
{Seattle, WA} % Location
{Nov. 2020 - Sept. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Leveraged Andro-guard to design new APK analysis capabilities for scaled malware detection}
    \item {Mentored junior analysts to develop their career}
    \item {In-depth analysis of the Facestealer family of APKs including development timeline to identified over 300 APKs actively stealing user accounts}
    \item {Re-architected internal Dynamic Analysis infrastructure used for identifying malicious applications at scale}
    \item {Developed automation libraries and toolkits for malware analysis workflows and report generation}
    \item {Collaborated with engineers to build authenticated intelligence CLI agent to improve engineer efficiency}
    \item {Reverse Engineering of Malware on (Windows, iOS, Android, macOS) to generate reports and signatures to prevent the spread of malware on Meta platforms}
    \item {Reverse Engineering of mobile SDKs (iOS and Android) to detect Ads fraud and abuse in third party applications}
    \item {Reverse Engineering mobile and native applications for vulnerability assessments to harden Meta owned enterprise endpoints and Oculus applications}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Product Security Engineer, Ecosystem Integrity Protection} % Job title
{Apple} % Organization
{Seattle, WA} % Location
{Mar. 2020 - Nov. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Lead and architected framework leveraging AWS and WWDR to prevent malicious applications from executing on macOS}
    \item {Unified analyst libraries and established engineering excellence on the team through deploying CI/CD and testing suites to code repository}
    \item {Reverse Engineered malware samples affecting macOS and published protective signatures deployed to endpoints}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Security Engineer, Detection Infrastructure} % Job title
{Facebook} % Organization
{Menlo Park, CA} % Location
{Feb. 2016 - Mar. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Core developer and maintainer of osquery project - https://osquery.io}
    \item {Lead security org to scale Endpoint Detection and Response infrastructure by migrating legacy on-prem infrastructure to cloud-hosted solution}
    \item {Lead enterprise endpoint security team to deploy Santa and AppLocker to corporate macOS and Windows endpoints}
    \item {Worked with security leadership to establsih a new team focusing on enterprise endpoint security}
    % Automated tier 1 and tier 2 SOC detections/responses through integration with 3rd party solution
    \item {Purchase and integration of third-party Detection-as-a-Service capabilities}
    \item {Developed and maintained host-based endpoint monitoring agents, logging infrastructure, and deployment mechanisms}
    \item {Administered and orchestrated Carbon Black backend infrastructure and endpoint deployment}
    \item {Built endpoint detections leveraging host-based telemetry}
    \item {Mentored university students internationally for the Facebook Open Source Mentorship program}
    % Scaled DNS Allow/Deny-listing capability 
    \item {Rearchitected corporate DNS deny-listing capability, increasing reliability and reducing operational overhead}
    \item {Developed and delivered security education curriculum for lockpicking and Capture The Flag challenges used in Hacktober security awareness month}
    \item {Developed and delivered osquery workshop curriculum for conferences to teach endpoint detection at scale}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Cyber Security R\&D Scientist and Engineer} % Job title
{Sandia National Laboratories} % Organization
{Albuquerque, NM} % Location
{Jan. 2015 - Jan. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Malware Reverse Engineer on Security Incident Response Teams}
    \item {Reverse Engineered and developed C2 generation script for detection of Hammertoss malware}
    \item {Mentored Albuquerque High School CyberPatriot team}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Graduate Student Intern, Center for Cyber Defenders (CCD)} % Job title
{Sandia National Laboratories} % Organization
{Albuquerque, NM} % Location
{June 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Developed fuzzing framework for email detection engine to test corporate detection rules}
    \item {Researched automated vulnerability discovery methods for Windows binary files}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Security Intern} % Job title
{Trail of Bits} % Organization
{New York, NY} % Location
{Jan. 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Developed platform testing framework for iterated Windows versions using Virtual Machine APIs}
\end{cvitems}
}

%------------------------------------------------
% Everything below here only displays for the Full CV mode
%------------------------------------------------

\begin{displaySection}
%------------------------------------------------

    \cventry
    {Software Developer, Systems Administrator} % Job title
    {Handel IT} % Organization
    {Laramie, WY} % Location
    {Sept. 2012 - Aug. 2013} % Date(s)
    { % Description(s) of tasks/responsibilities
    \begin{cvitems}
    \item {C\# and .NET software developer for RiteTrack5 software suite}
    \item {Systems Administrator for Windows 2003, 7, 2008, 2012, and FreeBSD(pfSense) Operating Systems}
    \item {Deployed and Administered Nagios Core to enterprise endpoints}
    \item {Administered Windows SCCM server for software deployments and endpoint compliances}
    \end{cvitems} 
    }

    \cventry
    {Academic Lecturer} % Job title
    {University of Wyoming, Mathematics Dept.} % Organization
    {Laramie, WY} % Location
    {Dec. 2009 - Apr. 2010} % Date(s)
    { % Description(s) of tasks/responsibilities
    \begin{cvitems}
    \item {Responsible for lectures, student grades, and preparing and issuing class quizzes}
    \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {IT Technicianfor Academic Support Unit} % Job title
    {University of Wyoming} % Organization
    {Laramie, WY} % Location
    {Feb. 2008 - July. 2009} % Date(s)
    { % Description(s) of tasks/responsibilities
    \begin{cvitems}
    \item {Troubleshooting computer issues, maintaining computer labs, and tech support}
    \end{cvitems}
    }

    %------------------------------------------------
\end{displaySection}

\end{cventries}
